Data Specialization for a Staged Lambda Calculus

### 2015-02-26 paper/figures/splitting-overview.tex
moved masking to last
figure tweaks

\textbf{Masking Partial Values ---
$\rtab \xi v \vsplito \mval i q$}
\begin{enumerate}
\item[] Input $\rtab \xi v$ is the residual table and partial value to be masked.
\item[] Immediate result $i$ is a monostaged value representing the first-stage
result.
\item[] Residual $q$ is a monostaged term representing the second-stage work
left to do.
\end{enumerate}

\textbf{Splitting Terms at World \bbtwo\ ---
$\splittwo e A p l r$}
\begin{enumerate}
\item[] Input $\coltwo e A$ is the \lang\ program to be split.
\item[] Precomputation $p$ is a monostaged term containing the program's first-stage computations.
\item[] Resumer $l.r$ is a monostaged term containing the program's second-stage computations.
\end{enumerate}

\textbf{Splitting Terms at World \bbonem\ ---
$\splitone e A c {l.r}$}
\begin{enumerate}
\item[] Input $\colmix e A$ is the \lang\ program to be split.
\item[] Combined result $c$ is a monostage term containing the program's first-stage computations.
\item[] Resumer $l.r$ is a monostage term containing the program's second-stage computations.
\end{enumerate}

@@

\centering
\setlength{\unitlength}{2.8pt}
\begin{tabular}{c|c}
{\Large \bf Splitting at World \bbonem} & 
{\Large \bf Splitting at World \bbtwo} \\ \hline

@@

\put(25,78){\makebox[50 \unitlength]{Splitting $\left(\splitonesym\right)$}}
\put(25,33){\makebox[50 \unitlength]{Masking $\left(\vsplito\right)$}}
\put(76,55){\parbox[l]{20 \unitlength}{Separated \\ Evaluation: \\$\reduce c {\tup{i,b}}$\\$q\equiv [b/l]r$ }}
\put(9,55){\parbox[r]{20 \unitlength}{Interleaved \\ Evaluation: \\$\diaone e \xi v$}}

@@

\put(25,78){\makebox[50 \unitlength]{Splitting $\left(\splittwosym\right)$}}
\put(76,55){\parbox[l]{20 \unitlength}{Separated \\ Evaluation: \\ $\reduce p b$\\$q\equiv [b/l]r$}}
\put(9,55){\parbox[r]{20 \unitlength}{Interleaved \\ Evaluation: \\ $\diatwo e q$}}

>>>>

\textbf{Splitting Terms at World \bbtwo\ ---
$\splittwo {\coltwo e A} A p l r$}
\begin{enumerate}
\item[] Precomputation $p$ is a monostaged term containing the first-stage computations in $e$.
\item[] Resumer $l.r$ is a monostaged term containing the second-stage computations in $e$.
\end{enumerate}

\textbf{Splitting Terms at World \bbonem\ ---
$\splitone {\colmix e A} A c {l.r}$}
\begin{enumerate}
\item[] Combined result $c$ is a monostage term containing the first-stage computations in $e$.
\item[] Resumer $l.r$ is a monostage term containing the second-stage computations in $e$.
\end{enumerate}

\textbf{Masking ---
$\rtab \xi v \vsplito \mval i q$}
\begin{enumerate}
\item[] Input $\rtab \xi v$ is the residual table and partial value to be masked.
\item[] Immediate value $i$ is a monostage value representing the first-stage components of $v$.
\item[] Residual $q$ is a monostaged term representing the second-stage computations in $\xi$ and $v$.
\end{enumerate}

@@

\centering
\setlength{\unitlength}{2.8pt}
\begin{tabular}{c|c}
{\large \bf Splitting at World \bbonem} & 
{\large \bf Splitting at World \bbtwo} \\

@@

\put(25,78){\makebox[50 \unitlength]{Splitting $\left(\splitonesym\right)$}}
\put(25,33){\makebox[50 \unitlength]{Masking $\left(\vsplito\right)$}}
\put(76,55){\parbox[l]{20 \unitlength}{Separated \\ Evaluation: \\$\reduce c {\tup{i,b}}$\\$q\equiv [b/l]r$ }}
\put(9,55){\parbox[r]{20 \unitlength}{First-Stage \\ \lang\ Eval.: \\$\diaone e \xi v$}}

@@

\put(25,78){\makebox[50 \unitlength]{Splitting $\left(\splittwosym\right)$}}
\put(76,55){\parbox[l]{20 \unitlength}{Separated \\ Evaluation: \\ $\reduce p b$\\$q\equiv [b/l]r$}}
\put(9,55){\parbox[r]{20 \unitlength}{First-Stage \\ \lang\ Eval.: \\ $\diatwo e q$}}
